An Implementation of the Active Contours without Edged model and the Logic Framework for Active contours on multi-channel images

### 2010-12-12 cs870/project/Report/Paper.tex
typo

\begin{equation}
\label{eqn:zin}
z_{i}^{in}(u_{0}^{i},x,y,C) = \frac{|u_{0}^{i} - c_{+}^i|^2}{(max^{2}_{(x,y) \in u_{0}^{i}} u_{0}^i)^2}
\end{equation}

@@

@@

@@

For the Sandberg-Chan model, the successful detection of boundaries criteria is implicitly

@@

@@

\subsubsection*{Union}

\subsubsection*{Intersection}

>>>>

\begin{equation}
\label{eqn:zin}
z_{i}^{in}(u_{0}^{i},x,y,C) = \frac{|u_{0}^{i} - c_{+}^i|^2}{(max_{(x,y) \in u_{0}^{i}} u_{0}^i)^2}
\end{equation}

@@

\begin{figure}[t]
\centering
\includegraphics[width=7cm]{sc_unionsimple.png}
\caption{}
\label{fig:sc_unionsimple}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=7cm]{sc_intersectionsimple.png}
\caption{}
\label{fig:sc_intersectionsimple}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=7cm]{threech.png}
\caption{}
\label{fig:threech}
\end{figure}

@@

For the Sandberg-Chan model, the successful detection of boundaries criteria is implicitly included in the logic operations functionality. We therefore, show
the other criteria.

\subsubsection*{Logic Operators: union and intersection}

To ensure that the union operator is working properly, we tried it on a very simple example of two rectangles shown in Figure~\ref{fig:sc_unionsimple}. The
union of the two rectangles was successfully detected. Similarly, Figure~\ref{fig:sc_intersectionsimple} shows the intersection for the same two simple
rectangles.

Figure~\ref{fig:donutlogic} shows a more complicated example for both the intersection and union with the donut image shown in the previous section. We used
two versions of the donuts with each one having a different part occluded. The results of the union and intersection operators are shown in the figure.
Additionally, this example shows that the Sandberg-Chan model can still successfully detect holes despite the addition of the logic operations.

A practical usage of this logic operations framework is to recover missing parts from different images, and combine them to produce a more complete image. We
show this in Figure~\ref{fig:family} which shows two different version of a family image with a child missing in each image. When the union is applied to these
two channels, the complete family image is recovered.

\begin{figure*}[t]
\centering
\includegraphics[width=12cm]{donutlogic.png}
\caption{}
\label{fig:donutlogic}
\end{figure*}

\begin{figure*}[t]
\centering
\includegraphics[width=12cm]{flowers.png}
\caption{}
\label{fig:threech}
\end{figure*}

@@

Similar to the previous model, we needed to ensure that the position of the initial curve does not alter our results. Figure~\ref{fig:sc_initialcurve} shows
the segmentation results obtained for the same image used in Figure~\ref{fig:sc_unionsimple}, but with a different position for the initial curve.

@@
